First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-24 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
update the paper with definitions of some varaibles

The photon-electroproduction cross section can be decomposed into a BH,
a DVCS, and an interference terms. At leading twist, the amplitudes of the 
three terms can be decomposed into a finite sum of Fourier harmonics, the 
so-called BMK formalism, as shown for the nucleon DVCS in 
\cite{Belitsky:2001ns} and for the spinless nuclei in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, the beam-spin asymmetry 
($A_{LU}$) with the two opposite helicities of a longitudinally-polarized 
electron beam (L) on a spin-zero target (U) can be written as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$.  
The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
nuclear form factor ($F_{A}(t)$) and the independent variables $Q^2$, $x_{B}$ 
and $t$. These factors are simplified as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in 
\cite{Belitsky:2008bz}. Therefore, Using the $\alpha_{i}$ factors, one can 
obtain in a totally model-independent way $\Im m(\mathcal{H}_{A})$ and $\Re 
e(\mathcal{H}_{A})$ from fitting the experimental $A_{LU}$ as a function of 
$\phi$, the azimuthal angle between the ($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) 
planes, for given values of $Q^2$, $x_{B}$, and $t$.

>>>>

The photon-electroproduction cross section can be decomposed into a BH,
a DVCS, and an interference terms. At leading twist, the amplitudes of the 
three terms can be decomposed into a finite sum of Fourier harmonics, the 
so-called BMK formalism, as shown for the nucleon DVCS in 
\cite{Belitsky:2001ns} and for the spinless nuclei in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, the beam-spin asymmetry 
($A_{LU}$) with the two opposite helicities of a longitudinally-polarized 
electron beam (L) on a spin-zero target (U) can be written as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
independent variables $Q^2$, $x_{B}$ and $t$. These factors are simplified as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. Their 
explicit expressions can be found in \cite{Belitsky:2008bz}.  Therefore, Using 
the $\alpha_{i}$ factors, one can obtain in a totally model-independent way 
$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from fitting the 
experimental $A_{LU}$ as a function of $\phi$ for given values of $Q^2$, 
$x_{B}$, and $t$.
